Verifying Demonstrations

### 2020-03-13 paper/distance-bounding.tex
Changes some equations to display, fixes bugs in eqns

\begin{definition}[Tainted session, \acs*{DBMF}~\cite{DB-DFKO}]%
  \label{TaintedMF}
  A time-critical round
  \(\Xscript{\sid}{k, k+1} = (m_k, \dotsc, m_{k+1})\)
  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
  verifier, is \emph{tainted} by the round
  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
  of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    (m_k, m_{k+1}) &= (m_{k'}, m_{k'+1}) \\
    \marker[\sid, k] &< \marker[\sid', k'] \\
    \marker[\sid, k+1] &> \marker[\sid', k'+1].
  \end{align*}
\end{definition}

@@

\Acl{DBTF} is similar to \ac{DBMF}, the difference is that during \ac{DBTF} the 
prover cooperates with the adversary to make the verifier accept.

>>>>

\begin{definition}[Tainted session, \acs*{DBMF}~\cite{DB-DFKO}]%
  \label{TaintedMF}
  A time-critical round \[
    \Xscript{\sid}{k, k+1} = (m_k, \dotsc, m_{k+1})
  \] of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
  verifier, is \emph{tainted} by the round \[
    \Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})
  \] of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    (m_k, m_{k+1}) &= (m_{k'}, m_{k'+1}) \\
    \marker[\sid, k] &< \marker[\sid', k'] \\
    \marker[\sid, k+1] &> \marker[\sid', k'+1].
  \end{align*}
\end{definition}

@@

\Acl{DBTF} is similar to \ac{DBMF}, the difference is that during \ac{DBTF} the 
prover cooperates with the adversary to make the verifier accept.
This means that we must disallow relay \emph{scheduling}: with 
\cref{TaintedMF}, the prover and adversary could relay a function of every 
answer, then the adversary could just apply the inverse function before sending 
the answer to the verifier.
